---
title: "Regression and Statistical Inference"
author: "Huzzaifa"
---

Assignment 1:


```{r}
cars_df = readRDS("C:/Users/huzai/OneDrive/Documents/GitHub/tes/cdsba-cdx3745/content/Causal_Data_Science_Data/Causal_Data_Science_Data/car_prices.rds.")

```
```{r}
dim(cars_df)
```

our data frame has 181 rows and 22 columns

Assignment 2:

```{r}
head(cars_df)

```
I see the two data types, double and character.double datatype are numerical values whereas the Character data types are string data.

Assignment 3:

```{r}
lm_cars_price <- lm(price ~ ., data = cars_df)
summary(lm_cars_price)
```

Considering the statistical significance and after viewing the summary of the model. I decide to chose the alpha = 0.05 and the factors or independent variables having p-values less than alpha are the relevant factors. Those are [ carbodyhardtops,carbodyhatchback, carbodywagon, enginelocationrear, carwidth, enginetypeOHC, enginetypeOHCV, cylindernumberfive, cylindernumberfour,cylindernumbersix, cylindernumbertwelve, enginesize, stroke and peakrpm ]

Assignment 4:

1. I chose "carwidth" as a regressor. It has the data type double and can take numerical values.

2.
```{r}
lm_price_CW <- lm(price ~ carwidth,data = cars_df)
summary(lm_price_CW)

```
By seeing the summary we can see our model comes out to be price_est = -174994 + 2859.5 * carwidth. That means if we have a rise of one unit in the carwidth than price would be increasiing by a factor of 2859.5.

3.

```{r}
sprintf("Adjusted R^2: %.2f", broom::glance(lm_cars_price)$adj.r.squared)
sprintf("Adjusted R^2: %.2f", broom::glance(lm_price_CW)$adj.r.squared)

sprintf("AIC: %.2f", AIC(lm_cars_price))
sprintf("AIC: %.2f", AIC(lm_price_CW))

sprintf("AIC: %.2f", BIC(lm_cars_price))
sprintf("AIC: %.2f", BIC(lm_price_CW))


```
As seen that the model considering only carwidth doesnot perform well as compared to the model with all parameter. The model with all factor have less AIC and BIC and greater adjusted R^2.

Assignment 5:

```{r}
library(dplyr)
cars_df %>%
  mutate(seat_heating = TRUE)
```

```{r}
lm_cars_price1 <- lm(price ~ ., data = cars_df)
summary(lm_cars_price1)
```
After adding a new variable to the data and as it has only a TRUE value for every sample which is constant that doesnot  impact our model and for that reason in the model summary section the Coefficents doesnot include it.
