---
title: "Directed Acyclic Graphs 5"
Author : "Huzzaifa Khan"
---

Assignment : 1

```{r}
library(dagitty)
library(ggdag)

collider <- dagify(
  D ~ Loc ,
  Y ~ Loc ,
  Y ~ D   ,
  

  
  coords = list(x = c(D = 1, Y = 3, Loc = 2),
                y = c(D = 1, Y = 1, Loc = 2))
)

# Plot DAG
ggdag(collider) 
```

Assignment : 2


```{r}
df_customer = readRDS("C:/Users/huzai/OneDrive/Documents/GitHub/tes/cdsba-cdx3745/content/Causal_Data_Science_Data/Causal_Data_Science_Data/customer_sat.rds.")

View(df_customer)

```

```{r}
head(df_customer)

```

1)-

```{r}
lm_sat <- lm(satisfaction ~ follow_ups, data = df_customer)
summary(lm_sat)
```

2)-

```{r}
lm_sat_all <-lm(satisfaction ~ ., data = df_customer)
summary(lm_sat_all)
```
Assignment : 3

when we consider only followup as a regressor for satisfaction than our relation is linear but in negative direction. However if we conisider the subscription as a regressor aswell, than the relation with followup is in opposite direction to satisfaction, than P-value is aslo higher. Subscription(subscriptionPremium, subscriptionPremium+) with very low P-value can be refered as confounder. value   that is more considerable when finding the cause of satisfcation  from followups


```{r}
library(ggplot2)

customers_satPlot <- ggplot(df_customer, aes(x = follow_ups , y = satisfaction)) +
geom_point(alpha = .8) +
stat_smooth(method = "lm", se = F)

# Conditioning on subscriptiomn
customers_satPlot2<- ggplot(df_customer, aes(x = follow_ups, y = satisfaction,
                            color = subscription, )) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  scale_alpha_manual(values = c("subscription" = 1, "no_subscription" = 0.2)) +
  theme(legend.position = "right")

# Plot both plots
customers_satPlot 
customers_satPlot2
```