---
title: "Instrumental Variables"
author: "Huzzaifa"
---

```{r}
user_df <- readRDS("C:/Users/huzai/OneDrive/Documents/GitHub/tes/cdsba-cdx3745/content/Causal_Data_Science_Data/Causal_Data_Science_Data/rand_enc.rds")

View(user_df)
```

```{r}
#Assignment: 1

library(dagitty)
library(ggdag)
library(ggplot2)

app_DAG <- dagify(
  X ~ U,
  Y ~ U,
  Y ~ X,
  X ~ Z,
  coords = list(x = c(Z = 0, Y = 3, U = 2, X = 1),
                y = c(Z = 0, Y = 0, U = 1, X = 0)),
  labels = list(X = "New Feature",
                Y = "Time spent", 
                Z = "Confounders",
                IV = "Popup_note")
)
# Plot DAG
ggdag(app_DAG) +
  theme_dag_gray() + # custom theme, can be left out
  geom_dag_point(color = "blue") +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))

```

```{r}
#Assignment: 2
model_full <- lm(time_spent ~ used_ftr, data = user_df)
summary(model_full)

```

```{r}
#Assignment: 3

# Correlation matrix
cor(user_df) %>% round(2)
```
- As shown by the correlation matrix our instrument variable "rand_enc" is less correlated to our treatment variable used feature, that implies we have a weak instrument relevance. To test this assumption there might be some better procedure
- Our instrument variable holds monotonically assumpotion as our correlation is positive
-Our IV holds Exclusion restriction as the corr bw IV and Outcome "time_spent" is very low

```{r}
#Assignment: 4

# First stage
first_stage <- lm(used_ftr ~ rand_enc, data = user_df)
summary(first_stage)
```

```{r}
# Second stage
second_stage <- lm(user_df$time_spent ~ first_stage$fitted.values)
summary(second_stage)
```

```{r}
library(estimatr)
model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = user_df)
summary(model_iv)
```

In my opinion naive approach has better estimate as compared to the IV approach. as the std. error is quite less in naive. I can think of 2 reasons:

1- there may exist a cofounding bw our IV and treatment variable.
2- With IV approach it might be that we get a better LATE estimate as there can be good IV variable whiich has more relevance to the treatment.